---
title: "Replication early analysis"
output: html_notebook
---

First we import data

```{r}
library(tidyverse)
library(grf)
library(haven)
source('best_tree.R')
source('baum_heuristic.R')

data <- read_dta('macoursetal_main.dta')
```

Variables have already been transformed which is excellent.

```{r}


X <- data[c('male', 's1age_head_05', 's1hhsize_05', 's1hhsz_undr5_05', 's1hhsz_5_14_05', 's1hhsz_15_24_05', 's1hhsz_25_64_05', 's1hhsz_65plus_05', 's1male_head_05', 'ed_mom_inter', 'ed_mom_miss', 'bweight_miss', 'bweight_inter', 'tvip_05_miss', 'tvip_05_inter', 'height_05_miss', 'height_05_inter', 'weight_05_miss', 'weight_05_inter', 'com_haz_05', 'com_waz_05', 'com_tvip_05', 'com_control_05', 'com_vit_05', 'com_deworm_05', 'com_notvip')]

Y <- data %>%
  select(contains('z_') & contains('_06') & -contains('_06m'))

W <- data$T

selectorXW <- complete.cases(X) & complete.cases(W)

X <- X[selectorXW,]
Y <- Y[selectorXW,]
W <- W[selectorXW]
```

We're going to remove incomplete cases for X (only 46 of them) and W (also 46 cases). However for Y where only 2% is complete, we will just omit cases where we don't have the outcome. First let's check where the missing data is though.

```{r}
map_dbl(Y, ~sum(is.na(.x)))
```

There is missing data in a lot of variables.


```{r}
forest_outputs <- Y %>%
  map(function (y) {
    selector <- !is.na(y)
    .y <- y[selector]
    .X <- X[selector,]
    .W <- W[selector]
    
    causal_forest(X = .X,
                 Y = .y,
                 W = .W
                     )}
      )
```

Next we'll use the Baum heuristic to extract a representative tree.

```{r}
baum_trees <- map(forest_outputs, ~baum_step_3(.x, data))
wager_trees <- map(forest_outputs, find_best_tree)
```


