---
title: "Replication early analysis"
output: html_notebook
---

First we import data

```{r}
library(tidyverse)
library(grf)
library(haven)
source('best_tree.R')
source('baum_heuristic.R')
source('prediction grf_tree.R')

data <- read_dta('macoursetal_main.dta')

# data <- data %>%
#   filter(TREAT1 == 1 | TREAT2 == 1)
```

Variables have already been transformed which is excellent.

```{r}
data <- data %>%
  mutate(s1hhsz_undr5_05_perc = s1hhsz_undr5_05 / s1hhsize_05,
    s1hhsz_5_14_05_perc = s1hhsz_5_14_05 / s1hhsize_05,
    s1hhsz_15_24_05_perc = s1hhsz_15_24_05 / s1hhsize_05,
    s1hhsz_25_64_05_perc = s1hhsz_25_64_05 / s1hhsize_05,
    s1hhsz_65plus_05_perc = s1hhsz_65plus_05 / s1hhsize_05,
)
```


```{r}


# X <- data[c('male', 's1age_head_05', 's1hhsize_05', 's1hhsz_undr5_05', 's1male_head_05', 'ed_mom_inter', 'bweight', 'tvip_05')]

X.unselect <- data[c(
  'male',
  'age_months_08',
  's1age_head_05',
  's1male_head_05',
  's1hhsize_05',
  'ed_mom',
  's1hhsz_undr5_05_perc',
  's1hhsz_5_14_05_perc',
  's1hhsz_15_24_05_perc',
  's1hhsz_25_64_05_perc',
  's1hhsz_65plus_05_perc',
  'bweight',
  'height_05',
  'weight_05',
  'tvip_05',
  'weighted_05',
  's4p7_parasite_i_05',
  's4p6_vitamina_i_05',
  'com_haz_05',
  'com_waz_05',
  'com_tvip_05',
  'com_control_05'
)]

Y <- data %>%
  select(z_all_08)

W <- data$T
```

```{r}

summary_vars <- data[c(
  'male',
  'age_months_08',
  's1age_head_05',
  's1male_head_05',
  's1hhsize_05',
  'ed_mom',
  's1hhsz_undr5_05_perc',
  's1hhsz_5_14_05_perc',
  's1hhsz_15_24_05_perc',
  's1hhsz_25_64_05_perc',
  's1hhsz_65plus_05_perc',
  'bweight',
  'height_05',
  'weight_05',
  'tvip_05',
  'weighted_05',
  's4p7_parasite_i_05',
  's4p6_vitamina_i_05',
  'com_haz_05',
  'com_waz_05',
  'com_tvip_05',
  'com_control_05',
  'T',
  'z_all_08'
)]

labels <- summary_vars %>% map_chr(~attributes(.)$label)

summary_stats <- map2_df(summary_vars, labels, summary)

row.names(summary_stats) <- labels

write.csv(summary_stats, 'summary_stats.csv')
```

```{r}
selectorXW <- complete.cases(W)

X <- X.unselect[selectorXW,]
Y <- Y[selectorXW,]
W <- W[selectorXW]
```

We're going to remove incomplete cases for X (only 46 of them) and W (also 46 cases). However for Y where only 2% is complete, we will just omit cases where we don't have the outcome. First let's check where the missing data is though.

```{r}
X %>%
  map_dbl(~sum(is.na(.x))/length(.x))
```

```{r}
X <- X %>%
  map_df(function(x){
    x[is.na(x)] <- mean(x, na.rm = TRUE)
    x
  })
```


```{r}
map_dbl(Y, ~sum(is.na(.x)))
```

There is missing data in a lot of variables.



```{r}
seed = 70123 #82199
set.seed(seed)

y <- Y$z_all_08

selector <- !is.na(y) #& y < 4 & y > -4
    .y <- y[selector]
    .X <- X[selector,]
    .W <- W[selector]
    
    y.hat = regression_forest(X=.X, Y=.y, seed=seed)$predictions
    # print(paste0('For ', y_names,' CATE is: ', mean(y.hat)))
    
    W.hat = regression_forest(X=.X %>% select(-starts_with('com')), Y=.W, seed=seed)$predictions
    
    X_treat <- .X %>%
      select(age_months_08,
        male,
        s1hhsz_undr5_05_perc,
        height_05,
        s4p7_parasite_i_05,
        ed_mom
)
    reg_data <- cbind(.y, X_treat, .W)
    linear_model <- lm(data = reg_data, .y ~ .)
    
    # linear_model_treat <- lm(data = reg_data %>% filter(T == 1), .y ~ .)
    # linear_model_control <- lm(data = reg_data %>% filter(T == 0), .y ~ .)
    
    forest_outputs <- list(z_all_08 = causal_forest(X = X_treat,
                 Y = .y,
                 W = .W,
                 Y.hat=y.hat,
	               W.hat=W.hat,
                 seed = seed,
                 sample.fraction = 0.8,
                 ci.group.size = 1,
                 min.node.size = 60))
                 
    cf05 <- causal_forest(X = X_treat,
                 Y = .y,
                 W = .W,
	               W.hat=W.hat,
                 seed = seed,
                 sample.fraction = 0.5,
                 ci.group.size = 1
                 
    )
    # return(regression_forest(X=.X, Y=.y, seed=seed))

```

Next we'll use the Baum heuristic to extract a representative tree.

Test tuning parameter

```{r}
# best_tree_tuning0 <- find_best_tree(forest_outputs$z_all_06, "causal", 0)
# 
# best_tree_tuning0.5 <- find_best_tree(forest_outputs$z_all_06, "causal", 0.5)
# 
# best_tree_tuning1 <- find_best_tree(forest_outputs$z_all_06, "causal", 1)
# 
# best_tree_tuning10 <- find_best_tree(forest_outputs$z_all_06, "causal", 10)
```

```{r}

# best_tree_est <- function (tree, cost) {
#   x <- find_best_tree(tree, "causal", cost)
#   
#   unfiltered_samples <- estimate_params(forest_outputs$z_all_06$X.orig,
#                 forest_outputs$z_all_06$Y.orig, 
#                 forest_outputs$z_all_06 %>% get_tree(x$best_tree),
#                 x$best_prune_info) %>%
#   map(~.x$samples)
#   
#   
#   valid_samples <- list()
# 
# i <- 1
# j <- 1
# 
# while (i <= length(samples)) {
#   if (!is.null(unfiltered_samples[[i]])) {
#     valid_samples[[j]] <- unfiltered_samples[[i]]
#     j <- j + 1
#   }
#   i <- i + 1
# }
# 
# valid_samples
# }
```

```{r}
# output_test0 <- best_tree_est(forest_outputs$z_all_06, 0)
# 
# output_test0.2 <- best_tree_est(forest_outputs$z_all_06, 0.2)
```


```{r}
baum_trees <- map(forest_outputs, ~baum_step_3(.x, data))
wager_trees <- map(forest_outputs, ~find_best_tree(.x, "causal"))

names(baum_trees) <- names(Y)
names(wager_trees) <- names(Y)
```


And show the parametres for the best tree on OOB

```{r}
Y.oob <- forest_outputs$z_all_08$Y.orig
X.oob <- forest_outputs$z_all_08$X.orig

best_tree_info <- wager_trees$z_all_08
best_tree_params <- estimate_params(X.oob, Y.oob, get_tree(forest_outputs$z_all_08,wager_trees$z_all_08$best_tree), wager_trees$z_all_08$best_prune_info)
```

Construct data frame with rules

```{r}
best_rules <- get_rule_list(get_tree(forest_outputs$z_all_08, best_tree_info$best_tree))

# Keep only the first row for each duplicate of z$id; this row will have the
# largest value for z$var
best_rules %>%
  map(function (x) {simplified_rules <- x[order(x$parents,  decreasing=TRUE),]
simplified_rules <- simplified_rules[!duplicated(simplified_rules$variable),]

simplified_rules
})
  
```

```{r}
get_tree(forest_outputs$z_all_08, best_tree_info$best_tree) %>% plot()
```

```{r}
best_parameters <- estimate_params(forest_outputs$z_all_08$X.orig,
                forest_outputs$z_all_08$Y.orig, 
                forest_outputs$z_all_08 %>% get_tree(wager_trees$z_all_08$best_tree),
                wager_trees$z_all_08$best_prune_info)
```

```{r}
pruned_baum <- baum_trees$z_all_08 %>%
  # forest_outputs$z_all_08 %>%
  # get_tree(wager_trees$z_all_08$best_tree) %>%
  prune_whole_tree(data, 30)

pruned_baum %>% plot()

samples <- pruned_baum %>%
  .$nodes %>%
  map(~.x$samples)

filter_valid_leaves <- function (samples1) {
  filtered_samples <- list()

  i <- 1
  j <- 1
  
  while (i <= length(samples1)) {
    if (!is.null(samples1[[i]])) {
      filtered_samples[[j]] <- samples1[[i]]
      j <- j + 1
    }
    i <- i + 1
  }
  filtered_samples
}

filter_valid_nodes <- function (samples1) {
  filtered_samples <- list()

  i <- 1
  j <- 1
  
  while (i <= length(samples1)) {
    if (!is.null(samples1[[i]])) {
      filtered_samples[[j]] <- samples1[[i]]
      j <- j + 1
    }
    i <- i + 1
  }
  filtered_samples
}

valid_samples <- filter_valid_leaves(samples)


data_used <- cbind(forest_outputs$z_all_08$X.orig,
                   forest_outputs$z_all_08$W.orig,
                   forest_outputs$z_all_08$Y.orig)

t.tests_leaves <- valid_samples %>%
  map(function (x) {
    leaf_data <- data_used[x,]
    
    leaf_treated <- filter(leaf_data, leaf_data$`forest_outputs$z_all_08$W.orig` == 1)
    
    leaf_control <- filter(leaf_data, leaf_data$`forest_outputs$z_all_08$W.orig` == 0)
    
    t.test(leaf_control$`forest_outputs$z_all_08$Y.orig`,
           leaf_treated$`forest_outputs$z_all_08$Y.orig`)
  })

leaf_results <- data.frame(difference = map_dbl(t.tests_leaves, ~.x$estimate %>% diff()),
           p.value = map_dbl(t.tests_leaves,~.x$p.value),
           stderr = map_dbl(t.tests_leaves,~.x$stderr),
           n = map_dbl(valid_samples, length)
)

write.csv(leaf_results, 'leaf_results.csv')
  
```



```{r}
# results <- finished_samples %>%
#   map(function (x) {
#     leaf_data <- data[x,]
#     
#     leaf_stats <- leaf_data %>%
#         group_by(T) %>%
#         summarise(count = n(),
#                   mean_Y = mean(z_all_08, na.rm = TRUE)
#       )
#     
#     leafw1 <- leaf_data %>% filter(T == 1)
#     leafw0 <- leaf_data %>% filter(T == 0)
#     
#     test <- t.test(leafw1$z_all_08, leafw0$z_all_08)
#     
#     list(leaf_stats = leaf_stats, test = test$p.value)
#   })
```

```{r}
# # Hardcoded analysis
# data_leaf_dist <- data[data %>%
#     select(s4p7_parasite_i_05, 
#            age_months_08, 
#            s1hhsz_undr5_05_perc,
#            T,
#            z_all_08
#     ) %>% complete.cases(),]
# 
# data_leaf_dist$leaf <- NA
# data_leaf_dist$leaf[data_leaf_dist$s4p7_parasite_i_05 != 1] <- 1
# 
# data_leaf_dist$leaf[(data_leaf_dist$s4p7_parasite_i_05 == 1) & (data_leaf_dist$age_months_08 > 59)] <- 2
# 
# data_leaf_dist$leaf[(data_leaf_dist$s4p7_parasite_i_05 == 1) & (data_leaf_dist$age_months_08 <= 59) & (data_leaf_dist$s1hhsz_undr5_05_perc > 0.22)] <- 3
# 
# data_leaf_dist$leaf[(data_leaf_dist$s4p7_parasite_i_05 == 1) & (data_leaf_dist$age_months_08 <= 59) & (data_leaf_dist$s1hhsz_undr5_05_perc <= 0.22)] <- 4
```

```{r}
# Map leaf distributions

data_used$Y.orig <- data_used$`forest_outputs$z_all_08$Y.orig`

data_used$W.orig <- data_used$`forest_outputs$z_all_08$W.orig`

data_used$leaf <- NA

for (i in 1:length(valid_samples)) {
  for (j in 1:length(valid_samples[[i]])) {
    data_used$leaf[valid_samples[[i]][j]] <- i
  }
}

data_used <- data_used[!is.na(data_used$leaf),]
```

```{r}
shapiros <- data_used %>%
  filter(Y.orig < 3.5, Y.orig > -3.5,
         !is.na(leaf)) %>%
  mutate(W.orig = ifelse(W.orig == 1, 'Treatment', 'Control')) %>%
  group_by(leaf, W.orig) %>%
  summarise(shapiro = shapiro.test(Y.orig)$p.value %>% 
              round(3) %>%
              format(digits=3, nsmall=3) %>%
              paste0('p = ', .)
              )

```


```{r}
data_used %>%
  filter(Y.orig < 3.5, Y.orig > -3.5,
         !is.na(leaf)) %>%
  mutate(W.orig = ifelse(W.orig == 1, 'Treatment', 'Control')) %>%
  ggplot(aes(x = Y.orig)) +
    geom_density() +
    facet_grid(rows = vars(leaf), cols = vars(W.orig)) +
    geom_text(data = shapiros, aes(x = -1.3, y = 1, label = shapiro)) +
    theme_minimal() +
    labs(title = 'Distributions of z normalised index of development \nindicators by leaf and treatment intention', caption = 'Note: excludes observations outside of 3.5 standard deviations from the mean', x = 'z normalised index of development indicators')

ggsave("normal.png", width = 5, height = 8)
```

```{r}
W.hat %>% qplot()
```

```{r}
forest_outputs$z_all_08 %>%
  average_treatment_effect()
```

```{r}
# forest_outputs$z_all_08 %>%
#   average_treatment_effect(subset = data_used$leaf == 1)
```


```{r}
data_used %>%
  group_by(W.orig) %>%
  summarise(mean(Y.orig))
```

```{r}
var_imp <- variable_importance(forest_outputs$z_all_08) %>%
  as.data.frame.matrix()

var_imp$varname <- colnames(forest_outputs$z_all_08$X.orig)

var_imp <- var_imp %>%
  arrange(desc(V1))

var_imp$varlabel <- c('Age in months (08 wave)', "Mother's education", "Height for age", "Gender", "Percentage of household\nunder 5", "Dewormed in past 6 months")

var_imp %>%
  ggplot(aes(x = varlabel, y = V1, label = format(V1, digits = 2))) +
  geom_col() + 
  labs(x = 'Variable name', y = 'Variable importance', caption = 'Note: All variables from baseline survey except age') + 
  geom_text(vjust = -1) +
  theme_minimal() +
  expand_limits(y = 0.5)

ggsave('var_imp.png', width = 10, height = 5)
```

```{r}
# average_treatment_effect(forest_outputs$z_all_08, subset = (forest_outputs$z_all_08$age_months_08 <= 66 & forest_outputs$z_all_08$male <= 0 & forest_outputs$z_all_08$
#                                                               s1hhsz_undr5_05_perc > 0.18))
```

```{r}
corrs <- .X %>%
  map_df(~as.numeric(.x)) %>%
  cor()
  
write.csv(corrs, 'correlations.csv')
```

```{r}
library(corrplot)

corrplot(corrs, method = "circle",
        title = "method = 'circle'",
        tl.pos = "n", mar = c(2, 1, 3, 1)) 
```


